\thesistitle

### 2019-08-25 sections/results.tex
Appendix
Various improvements

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a per location category.}
\label{tab:location}
\end{table}

We can see from these results that most clones are found at method level.

@@

\subsection{Relation}
Table~\ref{tab:relationref} shows our data regarding how different relations influence maintainability. We mark rows based on less than 100 refactorings red, as their result is less likely to have statistical significance. The \textbf{Relation} column refers to the relations introduced in Section~\ref{sec:setuprelation}. Relations are mutually exclusive so all percentages add up to 100\%. We use the following keywords as headers of the columns of our tables:
\begin{itemize}
  \item \textbf{Complexity}: The average delta complexity for all refactored clone classes in the specified category.
  \item \textbf{Parameters}: The average delta number of parameters for all refactored clone classes in the specified category.
  \item \textbf{Volume}: The average delta number of tokens for all refactored clone classes in the specified category.
  \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of data points we have for this category).
  \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
\end{itemize}
In this context, the \textit{delta} denotes the change in this metric between the before- and after-refactoring snapshot of the system, for each separate clone class that was refactored.

>>>>

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}). We can see from these results that nearly 80\% of clones are found at method level. 17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all). Constructors account for approximately 3\% of clones. In interfaces, only 1\% of clones is found.

\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a per location category.}
\label{tab:location}
\end{table}

@@

\subsection{Relation} \label{sec:resultsrelation}
Table~\ref{tab:relationref} shows our data regarding how different relations influence maintainability. We mark rows based on less than 100 refactorings red, as their result is less likely to have statistical significance. The \textbf{Relation} column refers to the relations introduced in Section~\ref{sec:setuprelation}. Relations are mutually exclusive so all percentages add up to 100\%. We use the following keywords as headers of the columns of our tables:
\begin{itemize}
  \item \textbf{Complexity}: The average delta complexity for all refactored clone classes in the specified category.
  \item \textbf{Parameters}: The average delta number of parameters for all refactored clone classes in the specified category.
  \item \textbf{Volume}: The average delta number of tokens for all refactored clone classes in the specified category.
  \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of data points we have for this category).
  \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
\end{itemize}
In this context, the \textit{delta} denotes the change in this metric between the before- and after-refactoring snapshot of the system, for each separate clone class that was refactored.
